\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-08-21 notes/2loopNLSM.tex
About to rearrange color dual bootstrap sections

\paragraph{Self-Dual Yang-Mills} The first example in the literature \cite{} of color-dual Feynman rules is that of Yang-Mills theory in the self-dual sector (SDYM):

@@

Using this definition on the final self-dual constraint equation thus yields the following equation of motion for the dynamical scalar field:

@@

\paragraph{YZ-Theory}
SDYM makes explicit reference to the spacetime dimension and Zakharov-Mikhailov theory, to be discussed in \sect{sec:ZMTheory}, does as well.
This makes both theories poorly suited for constructing dimensionally-regulated loop-level amplitudes.
On the other hand, YZ-theory is an honest $D$-dimensional theory that captures the classical physics of the nonlinear sigma model (NLSM) while manifest the duality between color and kinematics \cite{Cheung2016prv}.

@@

It is instructive to see how both of these constructions produce valid tree-level amplitudes for the pion. First we'll start with two $Y$ particles on legs 1 and 4. Applying the Feynman rules above, and plugging in on-shell states for the $Z$-particles produces the following $s$- and $t$-channel numerators:
n^{YY}_s &= (T^2T^3)_{14} = s_{12}^2 
 n^{YY}_t &=  F^{3}_{\,2|X}T^X_{14}  = s_{14}(s_{13}-s_{12})
Plugging these numerators into the ordered amplitudes $A(s,t)$ yields the desired result:
\be\label{eq:NLSMYZ4point}
A^{YY}_{(s,t)} = \frac{n^{YY}_s}{s_{12}}+\frac{ n^{YY}_t }{s_{14}} = s_{13}
Similarly we can do the same for the $Z$ and $\bar{Z}$ configuration. Below we have plugged in the on-shell $Z$-particle states, but have left the $\bar{Z}$ index free. This produces the following numerators:
n^{\bar{Z}Z}_s &= {}_4(F^{3}F^{2})_{1} =  s_{12}(s_{14}-s_{13})p_2^{\mu_1}+s_{12}^2(p_3-p_4)^{\mu_1}
 n^{\bar{Z}Z}_t &=   {}_2(F^{3}F^{4})_{1}  = s_{14}(s_{12}-s_{13})p_4^{\mu_1}+s_{14}^2(p_3-p_2)^{\mu_1}
where we have defined the short hand notation:
{}_x(F^{a_1}F^{a_2}\cdots F^{a_n})_{y} \equiv F^{a_1}_{\,x|b_2}F^{a_2}_{\,b_2|b_3}\cdots F^{a_n}_{\,b_n|y}
Similarly, we find the following ordered amplitude when plugging in these numerators:
A^{\bar{Z}Z}_{(s,t)} = \frac{n^{\bar{Z}Z}_s}{s_{12}}+\frac{ n^{\bar{Z}Z}_t }{s_{14}} = -s_{13}(p_2+p_3+p_4)^{\mu_1} = s_{13} \,p_1^{\mu_1}
Plugging in the on-shell polarizatoin of the conjugate field in \eqn{eq:onShellZStates} produces precisely the desired result of \eqn{eq:NLSMYZ4point}. Indeed, this construction is valid to all orders at tree-level. One can see this by considering the only two possible factorization channels the contribute the each of these amplitudes, the $YY$ cut and the $\bar{Z}Z$ cut:
A(...,Y,...,Y,...) &\rightarrow A(...,Y,...,Y)A(Y,...,Y,...)
&\rightarrow A(...,Y,...,Y,...,Z)A(\bar{Z},...)
Both factorization channels are valid descriptions of NLSM amplitudes when plugging in the $Z$ and $\bar{Z}$ on-shell states. As constructed, the $Y$ and $\bar{Z}$ particles may be off-shell, while the $Z$ particles must be placed on shell, $\varepsilon^Z_\mu(k)\rightarrow k_\mu$ in order for these numerators to produce NLSM ordered amplitudes. Given this special property of YZ-theory (namely that the $Z\bar{Z}$ and $YY$ constrctions are equivalent), the $Y$ particle need not be considered when constructing NLSM amplitudes on shell. This is essentially what $J$-thepory does, as we will show below.
\paragraph{J-theory} There is an alternative color-dual formulation of NLSM that the theory manifestly corresponds to NLSM at least at tree level \cite{Cheung:2021zvb}.
For related formulations of NLSM that do not treat color-kinematics duality see \cite{Freedman:1980us, Slavnov:1971mz}.
The construction begins with a first order formulation of NLSM in terms of chiral currents $J^\mu$.
First order formulation of NLSM in terms of chiral current $J^\mu$.
Two equations.
Two constraints, the field strength should vanish
\label{eq:FieldStrengthJ}
F_{\mu\nu}(J) = \partial_\mu J_\nu - \partial_\nu J_\mu + g[J_\mu , J_\nu]=0
which then implies that $J^\mu$ is pure gauge $J_\mu = U \partial_\mu U^{-1}$.
The second condition is that the chiral current should be in Lorenz gauge
\label{eq:LorenzGaugeJ}
\partial_\mu J^\mu=0
which then yields the NLSM equation of motion $\partial_\mu (U \partial^\mu U^{-1})=0$.
Taking a linear combination of \eqref{eq:FieldStrengthJ} and \eqref{eq:LorenzGaugeJ} yields
\label{eq:JTheoryEOM}
\Box J^\mu +g f^{abc} J^\nu \partial_\nu J^\mu = 0.
Integrating in an auxiliary field $\bar{J}^\mu$ as a Lagrange multiplier trivially produces the Lagrangian
\mathcal{L}^{\text{J}} =\bar{J}^\mu \Box J_\mu +g f^{abc} \bar{J}^\mu J^\nu \partial_\nu J^\mu .
By calculating an off-shell 4pt correlation function it is possible to check that this Lagrangian automatically satisfies color-kinematics duality.
Kinematic algebra is diff algebra (as usual).
How to extract physical states... (longitudinal J, weird J bar, restores broken Bose).

@@

\draftnoteJM{Put comment about the fact that you can use funny propagators without affecting CK earlier.  Mention NANS as modification of J-theory.}

\paragraph{ZM-theory}
\label{sec:ZMTheory}
While J-theory manifests color-kinematics duality, it only does so at tree level because J-theory breaks manifest Bose symmetry.
Manifest color-kinematics duality can be achieved at all loop orders by restricting J-theory to two spacetime dimensions where the chiral current can be dualized to a scalar $J^\mu = \epsilon^{\mu\nu} \partial_\nu \varphi$, which trivially enforces Lorenz gauge.
After plugging $\varphi$ into \eqref{eq:JTheoryEOM} and rearranging, another copy of $\varphi$ (rather than some new field) can be integrated in to obtain the Zakharov-Mikhailov (ZM) Lagrangian
\begin{eBox}
\be
\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2 + g f^{abc} \varphi^a (\partial^\mu \varphi^b)( \tilde{\partial}_\mu \varphi^c) =  \text{tr}\left[\frac{1}{2}(\partial \varphi)^2-i g \varphi [\partial_t \varphi, \partial_z \varphi ]\right]
\ee
\end{eBox}
where $\tilde{\partial}_\mu = \epsilon_{\mu\nu}\partial^\nu $.
This procedure makes it clear that ZM and NLSM encode the same classical physics, that is, their equations of motion are dual to each other.
The color-stripped Feynman rule for the three-point vertex can be read off from the Lagrangian, giving
\be
\langle ab\rangle \equiv p_a^\mu \epsilon_{\mu\nu} p_b^\nu =p_a^0 p_b^1 - p_a^1 p_b^0 = -\langle ba \rangle .
\ee
The vertex is (1) functionally symmetric and (2) the kinematic portion of the vertex is completely anti-symmetric: 
\be
\cubic{hgrey0}{}{nhpBlue}{}{nhpBlue}{}{nhpBlue} = \langle 12\rangle = \langle 23\rangle = \langle 31\rangle = -\langle 21\rangle
\ee
This important property is due to momentum conservation alone and does not need any additional kinematic constraints to satisfy the duality.
To prove off-shell color kinematics duality for any multiplicity and loop order it is enough to observe that the sum of the off-shell $s$-, $t$-, and $u$-channel numerators sum to zero
\be
\label{eq:ZMJacobi}
\langle ab \rangle \langle cd\rangle +\langle ac \rangle \langle db\rangle +\langle ad \rangle \langle bc\rangle =0 % \delta^{[a}_c\delta^{b]}_d + \delta^{[a}_d\delta^{c]}_b+ \delta^{[a}_b\delta^{d]}_c
\ee
by virtue of the 2D Levi-Civita identity $\epsilon_{\mu\nu}\epsilon_{\rho\sigma} = \eta_{\mu\rho}\eta_{\nu\sigma}-\eta_{\mu\sigma}\eta_{\nu\rho}$.
Amusingly, \eqref{eq:ZMJacobi} is simply a manifestation of the Schouten identity.

Since ZM theory manifested color-kinematics duality without any reference to the on-shell condition, a mass term can be added to ZM theory without spoiling color-kinematics duality.
In fact, the kinetic term could be dramatically altered.
In general, if the on-shell conditions are not used, color-kinematics duality admits any kinetic term but the choice of propagator might spoil locality in the double-coppied theory.

Later in this section we will show that the interaction vertex is precisely that belonging to self-dual Yang-Mills (SDYM) theory in light-cone gauge. However, as we'll see, the kinetic term for these two theories differ -- the SDYM kinetic term transmutes between the holomorphic field $\Phi$, and the anti-holomorphic field, $\bar{\Phi}$, while the ZM scalar leaves the kinematic sector untouched. this is a critical distinction between the two theories that has important consequences for their color-dual constructions at loop-level.

@@

@@

\paragraph{Generalities of known color-dual theories -- James (I'll come back to this later)}
\begin{itemize}
\item There's also CS but the amplitudes are all zero (and marginally 10D N=1 SYM)
\item All of the theories described above have diff as kinematic algebra
\item All of the theories choose a simple gauge like Lorenz or lightcone
\item All of the theories place some constraint on the field strength directly and get their equations of motion directly from that constraint, not the YM EOM.
\item (Almost all of the theories (aside from NLSM) have trivial amplitudes at least at tree level)
\item This means that almost all of the theories only have CK at the classical level, which can sometimes be fudged into 1-loop as we'll now discuss.
\end{itemize}

@@

\subsection{Notes to self}
\begin{itemize}
\item Mention NANS after j theory.  Color kinematics duality doesn't care about the propagator but using a funny one might mess up locality in the double copied theory.
\item We should comment on 1-loop YM.  Can you easily write down the $n$-gon numerator?  I have some memory that someone has some complicated YM numerator.
\item Are you sure that the SDYM EOM doesn't come from just $F=\epsilon F$?  If $A=\partial \Phi$ then $F$ has the right number of derivatives to give the SDYM EOM but $DF$ has too many.
\item Write Lagrangian for j-theory and reiterate the argument about why you know it's pions.  Reiterate connection to ZM (dualize j and integrate in phi).  Should probably mention CS somewhere.  Point out that all of the theories that come from have CK are really some version of YM where you (1) impose some condition like F=0 or some other condition on the field strength and (2) you impose Lorenz gauge.  Point out that the kinematic algebra is always diffs.
\item Cite papers arguing about whether NLSM in 2D is non-trivial or not.
\item Explain why you need to take a certain portion of the YZ numerator to get the right answer.  Basically you can't have a vector particle circle the loop -- NLSM is a scalar theory so only scalar DOF should actually live in cuts.  If you have a tree then you plug in longitudinal modes but if you have a loop then you really need to remove vector modes so that only scalars circle the loop.
\item Reiterate that the (tree) amplitudes of CS and SDYM are zero.
\item ZM and 2D NLSM (PCM) are the same classically but not quantum mechanically.
This observation is due to other people but an easy way to see it.
ZM and 2D NLSM have the same EOM after a field redefinition.
This means that the classical physics is the same but of course the Lagrangians aren't the same and the field redefinition can change the path integral measure.
\item Forcing pions to match ZM in 2D does funny things.
The pion coupling constant is dropped but is implicitly set by the ordered 4pt amplitude which is normalized to be $-k_1 \cdot k_3$ in the package.
I've tabulated what happens when you take a general D NLSM answer and force it to match ZM in 2D.
Let's say that $n_\text{NLSM} = z n_\text{ZM}$ in 2D where I'm matching basis/master numerators.
For 4pt tree, $z=2/3$ (I matched the half ladder).
For 4pt 1-loop, $z$ is free/pure generalized gauge (I matched the box).
For 4pt 2-loop (when you impose certain $\ell$ power counting) $z$ is $216/565=\tfrac{2^3 3^3}{5 \cdot 113}$ (I matched the double box and penta-triangle).
For 6pt tree, $z$ is 12/35 (I matched the half ladder).
So you can match kinematic structure (the combination of Mandelstams) of NLSM to ZM in 2D but you can't get the coupling constant right at loop level, that is, ZM is a different theory quantum mechanically.
Actually these numbers make it look like you can't even match the theories classically but I guess for the theories to match classically you only need the amplitudes to agree and I matched numerators.
\item Explain how matching to ZM is a little silly.
Check that NLSM and ZM numerator agree on cuts.
Can't do that or else it becomes subtle.
Only well defined object is numerator.
\item At 4pt 1-loop $\prod p_L^2 -p_R^2$ agrees with the ZM answer $\prod p_L \eps p_R$ up to some number.
At 6pt 1-loop this is not true and the two answers differ by alternating signs depending on the kinematic configuration.
\item You cannot lift ZM to general D NLSM in the democratic way that Nic described because it fails at 6pt tree.  So you take the ZM answer that looks like $\langle 1 2\rangle \langle 3 4\rangle...$ you can convert every pair of angles to dot products using 2D $\epsilon$ identities.  Make an ansatz where you do every pairing of $\epsilon$'s.  This doesn't work.
\item To clean up the NLSM 4pt 2-loop answer I forced the answer to match ZM in 2D.
The ZM answer also only has certain powers of loop momenta $\ell^5$...$\ell^8$ where $\ell$ represents any combination of $\ell_1$ and $\ell_2$.
I enforce this $\ell^5$...$\ell^8$ behavior on the NLSM ansatz too.
\item Describe Jacobi:  s,t,u channel color factors sum to zero so you want numerators to do the same
\item Remember that I've explicitly checked the nice form of the 1-loop NLSM numerators at 4pt, 6pt, and 8pt.
\item Should probably give the 4pt pion amplitude somewhere to show my conventions.
\end{itemize}

>>>>

\draftnoteJM{I believe this Lagrangian has a name -- BF theory.  All this does is set F=0 and if you impose Lorenz gauge then you get many of the known color-dual theories.}
\subsubsection{Self-Dual Yang-Mills} The first example in the literature \cite{} of color-dual Feynman rules is that of Yang-Mills theory in the self-dual sector (SDYM):

@@

Using this definition on the final \draftnoteJM{first?} self-dual constraint equation thus yields the following equation of motion for the dynamical scalar field:

@@

\subsubsection{YZ-Theory}
SDYM makes explicit reference to the spacetime dimension and Zakharov-Mikhailov theory, to be discussed in \sect{sec:ZMTheory}, does as well.
This makes both theories poorly suited for constructing dimensionally-regulated loop-level amplitudes.
On the other hand, YZ-theory is an honest $D$-dimensional theory that captures the classical physics of the nonlinear sigma model (NLSM) while manifest the duality between color and kinematics \cite{Cheung2016prv}.

@@

It is instructive to see how both of these constructions produce valid tree-level amplitudes for the pion. First we'll start with two $Y$ particles on legs 1 and 4. Applying the Feynman rules above, and plugging in on-shell states for the $Z$-particles produces the following $s$- and $t$-channel numerators:
\begin{align}
n^{YY}_s &= (T^2T^3)_{14} = s_{12}^2 
\\
 n^{YY}_t &=  F^{3}_{\,2|X}T^X_{14}  = s_{14}(s_{13}-s_{12})
\end{align}
Plugging these numerators into the ordered amplitudes $A(s,t)$ yields the desired result:
\be\label{eq:NLSMYZ4point}
A^{YY}_{(s,t)} = \frac{n^{YY}_s}{s_{12}}+\frac{ n^{YY}_t }{s_{14}} = s_{13}
\ee
Similarly we can do the same for the $Z$ and $\bar{Z}$ configuration. Below we have plugged in the on-shell $Z$-particle states, but have left the $\bar{Z}$ index free. This produces the following numerators:
\begin{align}
n^{\bar{Z}Z}_s &= {}_4(F^{3}F^{2})_{1} =  s_{12}(s_{14}-s_{13})p_2^{\mu_1}+s_{12}^2(p_3-p_4)^{\mu_1}
\\
 n^{\bar{Z}Z}_t &=   {}_2(F^{3}F^{4})_{1}  = s_{14}(s_{12}-s_{13})p_4^{\mu_1}+s_{14}^2(p_3-p_2)^{\mu_1}
\end{align}
where we have defined the short hand notation:
\be
{}_x(F^{a_1}F^{a_2}\cdots F^{a_n})_{y} \equiv F^{a_1}_{\,x|b_2}F^{a_2}_{\,b_2|b_3}\cdots F^{a_n}_{\,b_n|y}
\ee
Similarly, we find the following ordered amplitude when plugging in these numerators:
\be
A^{\bar{Z}Z}_{(s,t)} = \frac{n^{\bar{Z}Z}_s}{s_{12}}+\frac{ n^{\bar{Z}Z}_t }{s_{14}} = -s_{13}(p_2+p_3+p_4)^{\mu_1} = s_{13} \,p_1^{\mu_1}
\ee
Plugging in the on-shell polarizatoin of the conjugate field in \eqn{eq:onShellZStates} produces precisely the desired result of \eqn{eq:NLSMYZ4point}. Indeed, this construction is valid to all orders at tree-level. One can see this by considering the only two possible factorization channels the contribute the each of these amplitudes, the $YY$ cut and the $\bar{Z}Z$ cut:
\begin{align}
A(...,Y,...,Y,...) &\rightarrow A(...,Y,...,Y)A(Y,...,Y,...)
\\
&\rightarrow A(...,Y,...,Y,...,Z)A(\bar{Z},...)
\end{align}
Both factorization channels are valid descriptions of NLSM amplitudes when plugging in the $Z$ and $\bar{Z}$ on-shell states. As constructed, the $Y$ and $\bar{Z}$ particles may be off-shell, while the $Z$ particles must be placed on shell, $\varepsilon^Z_\mu(k)\rightarrow k_\mu$ in order for these numerators to produce NLSM ordered amplitudes. Given this special property of YZ-theory (namely that the $Z\bar{Z}$ and $YY$ constrctions are equivalent), the $Y$ particle need not be considered when constructing NLSM amplitudes on shell. This is essentially what $J$-thepory does, as we will show below.

\subsubsection{J-theory} There is an alternative color-dual formulation of NLSM that the theory manifestly corresponds to NLSM at least at tree level \cite{Cheung:2021zvb}.
For related formulations of NLSM that do not treat color-kinematics duality see \cite{Freedman:1980us, Slavnov:1971mz}.
The construction begins with a first order formulation of NLSM in terms of chiral currents $J^\mu$.
First order formulation of NLSM in terms of chiral current $J^\mu$.
Two equations.
Two constraints, the field strength should vanish
\be
\label{eq:FieldStrengthJ}
F_{\mu\nu}(J) = \partial_\mu J_\nu - \partial_\nu J_\mu + g[J_\mu , J_\nu]=0
\ee
which then implies that $J^\mu$ is pure gauge $J_\mu = U \partial_\mu U^{-1}$.
The second condition is that the chiral current should be in Lorenz gauge
\be
\label{eq:LorenzGaugeJ}
\partial_\mu J^\mu=0
\ee
which then yields the NLSM equation of motion $\partial_\mu (U \partial^\mu U^{-1})=0$.
Taking a linear combination of \eqref{eq:FieldStrengthJ} and \eqref{eq:LorenzGaugeJ} yields
\be
\label{eq:JTheoryEOM}
\Box J^\mu +g f^{abc} J^\nu \partial_\nu J^\mu = 0.
\ee
Integrating in an auxiliary field $\bar{J}^\mu$ as a Lagrange multiplier trivially produces the Lagrangian
\begin{eBox}
\be
\mathcal{L}^{\text{J}} =\bar{J}^\mu \Box J_\mu +g f^{abc} \bar{J}^\mu J^\nu \partial_\nu J^\mu .
\ee
\end{eBox}
By calculating an off-shell 4pt correlation function it is possible to check that this Lagrangian automatically satisfies color-kinematics duality.
Kinematic algebra is diff algebra (as usual).
How to extract physical states... (longitudinal J, weird J bar, restores broken Bose).

@@

\subsubsection{Zakharov-Mikhailov theory}
\label{sec:ZMTheory}
While J-theory manifests color-kinematics duality, it only does so at tree level because J-theory breaks manifest Bose symmetry.
Manifest color-kinematics duality can be achieved at all loop orders by restricting J-theory to two spacetime dimensions where the chiral current can be dualized to a scalar $J^\mu = \epsilon^{\mu\nu} \partial_\nu \varphi$, which trivially enforces Lorenz gauge.
After plugging $\varphi$ into \eqref{eq:JTheoryEOM} and rearranging, another copy of $\varphi$ (rather than some new field) can be integrated in to obtain the Zakharov-Mikhailov (ZM) Lagrangian
\begin{eBox}
\be
\label{eq:ZMLagrangian}
\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2 + g f^{abc} \varphi^a \epsilon^{\mu\nu}(\partial_\mu \varphi^b)( \partial_\nu \varphi^c) =  \text{tr}\left[\frac{1}{2}(\partial \varphi)^2-i g \varphi [\partial_t \varphi, \partial_z \varphi ]\right] .
\ee
\end{eBox}
This procedure makes it clear that ZM and NLSM encode the same classical physics, that is, their equations of motion are dual to each other.
ZM theory can also be tenuously motivated from SDYM theory.
The power counting of the interaction term in the SDYM equation of motion \eqref{SDEOM} makes it clear that the theory is critical in 2D.
This suggests that the two lightcone coordinates $u$ and $w$ should be identified as the coordinates of the 2D space.
The 4D d'Alembertian in lightcone coordinates, $\Box = 4 (\partial_u \partial_v - \partial_w \partial_{\bar{w}})$, cannot be interpreted as the 2D equivalent, so the kinetic term of SDYM must be scrapped and replaced with the correct 2D version.
This argument should be understood purely as an alternative route to ZM theory.
While NLSM and ZM are the same theory classically when restricted to 2D, SDYM and ZM are not because, for example, the tree amplitudes of SDYM vanish but those of ZM do not (cite argumentative papers).

The color-stripped Feynman rule for the three-point vertex can be read off from the Lagrangian \eqref{eq:ZMLagrangian}, giving
\be
\langle ab\rangle \equiv p_a^\mu \epsilon_{\mu\nu} p_b^\nu =p_a^0 p_b^1 - p_a^1 p_b^0 = -\langle ba \rangle .
\ee
The vertex is (1) functionally symmetric and (2) the kinematic portion of the vertex is completely anti-symmetric: 
\be
\cubic{hgrey0}{}{nhpBlue}{}{nhpBlue}{}{nhpBlue} = \langle 12\rangle = \langle 23\rangle = \langle 31\rangle = -\langle 21\rangle
\ee
This important property is due to momentum conservation alone and does not need any additional kinematic constraints to satisfy the duality.
To prove off-shell color kinematics duality for any multiplicity and loop order it is enough to observe that the sum of the off-shell $s$-, $t$-, and $u$-channel numerators sum to zero
\be
\label{eq:ZMJacobi}
\langle ab \rangle \langle cd\rangle +\langle ac \rangle \langle db\rangle +\langle ad \rangle \langle bc\rangle =0 % \delta^{[a}_c\delta^{b]}_d + \delta^{[a}_d\delta^{c]}_b+ \delta^{[a}_b\delta^{d]}_c
\ee
by virtue of the 2D Levi-Civita identity $\epsilon_{\mu\nu}\epsilon_{\rho\sigma} = \eta_{\mu\rho}\eta_{\nu\sigma}-\eta_{\mu\sigma}\eta_{\nu\rho}$.
Amusingly, \eqref{eq:ZMJacobi} is simply a manifestation of the Schouten identity.

Since ZM theory manifested color-kinematics duality without any reference to the on-shell condition, a mass term can be added to ZM theory without spoiling color-kinematics duality.
In fact, the kinetic term could be dramatically altered.
In general, if the on-shell conditions are not used, color-kinematics duality is unaffected by the details of the propagator structure.
Of course, dramatically altering the pole structure could spoil locality in the double-coppied theory.
As already mentioned, the only difference classically between ZM and SDYM is the propagator structure.
While both theories are color dual for the same reason, altering the propagators has profound consequences since SDYM tree amplitudes vanish and manifest color-kinematics does not persist to all loop orders.
Color dual theories with the same interactions but different kinetic terms have appeared in the literature before.
For example, J-theory and the theory of non-Abelian fluids presented in \cite{Cheung:2020djz} differ only in their propagators.
Specifically, taking the static limit of the fluid's $(D+1)$-dimensional kinetic term $\partial_t - \nabla^2$ and Wick rotating one of the coordinates yields the relativistic d'Alembertian of $D$-dimensional J-theory.

@@

\subsubsection{Wess-Zumino-Witten theory -- James}
I want to write this down or I'm going to completely forget it

\subsubsection{Chern-Simons theory -- James}
We won't use this but it's useful to treat all of the CK theories in one place
Cite Henrik Maor
Again you place some constraint on the field strength and use Lorenz gauge

\subsubsection{Generalities of known color-dual theories -- James}
Should this section maybe go first?

\begin{itemize}
\item There's also CS but the amplitudes are all zero (and marginally 10D N=1 SYM)
\item All of the theories described above have diff as kinematic algebra
\item All of the theories choose a simple gauge like Lorenz or lightcone
\item All of the theories place some constraint on the field strength directly and get their equations of motion directly from that constraint, not the YM EOM.
\item (Almost all of the theories (aside from NLSM) have trivial amplitudes at least at tree level)
\item This means that almost all of the theories only have CK at the classical level, which can sometimes be fudged into 1-loop as we'll now discuss.
\item For off-shell CK, the kinetic term is relatively unimportant so long as the poles are correctly/consistently identified (what do you mean by s,t,u channel poles).  This might screw up locality in the squared theory.
\end{itemize}

@@

@@

\subsection{Notes to self}
\begin{itemize}
\item We should comment on 1-loop YM.  Can you easily write down the $n$-gon numerator?  I have some memory that someone has some complicated YM numerator.
\item Cite papers arguing about whether NLSM in 2D is non-trivial or not.
\item Explain why you need to take a certain portion of the YZ numerator to get the right answer.  Basically you can't have a vector particle circle the loop -- NLSM is a scalar theory so only scalar DOF should actually live in cuts.  If you have a tree then you plug in longitudinal modes but if you have a loop then you really need to remove vector modes so that only scalars circle the loop.
\item Reiterate that the (tree) amplitudes of CS and SDYM are zero.
\item ZM and 2D NLSM (PCM) are the same classically but not quantum mechanically.
This observation is due to other people but an easy way to see it.
ZM and 2D NLSM have the same EOM after a field redefinition.
This means that the classical physics is the same but of course the Lagrangians aren't the same and the field redefinition can change the path integral measure.
\item Forcing pions to match ZM in 2D does funny things.
The pion coupling constant is dropped but is implicitly set by the ordered 4pt amplitude which is normalized to be $-k_1 \cdot k_3$ in the package.
I've tabulated what happens when you take a general D NLSM answer and force it to match ZM in 2D.
Let's say that $n_\text{NLSM} = z n_\text{ZM}$ in 2D where I'm matching basis/master numerators.
For 4pt tree, $z=2/3$ (I matched the half ladder).
For 4pt 1-loop, $z$ is free/pure generalized gauge (I matched the box).
For 4pt 2-loop (when you impose certain $\ell$ power counting) $z$ is $216/565=\tfrac{2^3 3^3}{5 \cdot 113}$ (I matched the double box and penta-triangle).
For 6pt tree, $z$ is 12/35 (I matched the half ladder).
So you can match kinematic structure (the combination of Mandelstams) of NLSM to ZM in 2D but you can't get the coupling constant right at loop level, that is, ZM is a different theory quantum mechanically.
Actually these numbers make it look like you can't even match the theories classically but I guess for the theories to match classically you only need the amplitudes to agree and I matched numerators.
\item Explain how matching to ZM is a little silly.
Check that NLSM and ZM numerator agree on cuts.
Can't do that or else it becomes subtle.
Only well defined object is numerator.
\item At 4pt 1-loop $\prod p_L^2 -p_R^2$ agrees with the ZM answer $\prod p_L \eps p_R$ up to some number.
At 6pt 1-loop this is not true and the two answers differ by alternating signs depending on the kinematic configuration.
\item You cannot lift ZM to general D NLSM in the democratic way that Nic described because it fails at 6pt tree.  So you take the ZM answer that looks like $\langle 1 2\rangle \langle 3 4\rangle...$ you can convert every pair of angles to dot products using 2D $\epsilon$ identities.  Make an ansatz where you do every pairing of $\epsilon$'s.  This doesn't work.
\item To clean up the NLSM 4pt 2-loop answer I forced the answer to match ZM in 2D.
The ZM answer also only has certain powers of loop momenta $\ell^5$...$\ell^8$ where $\ell$ represents any combination of $\ell_1$ and $\ell_2$.
I enforce this $\ell^5$...$\ell^8$ behavior on the NLSM ansatz too.
\item Describe Jacobi:  s,t,u channel color factors sum to zero so you want numerators to do the same
\item Remember that I've explicitly checked the nice form of the 1-loop NLSM numerators at 4pt, 6pt, and 8pt.
\item Should probably give the 4pt pion amplitude somewhere to show my conventions.
\end{itemize}
